---
title: "IODS course project"
author: "Sami Myllyniemi"
output:
  html_document:
    theme: cosmo
    toc: true
    toc_depth: 2
    fig_caption: true
    fig_width: 6
    fig_height: 4
    code_folding: hide
---
'TESTI
pnorm(15, 15, 3.2)

***
  
```{r child = "chapter1.Rmd"}
```
  
***
  
```{r child = "chapter2.Rmd"}
```

***
pnorm(15, 15, 3.2)
fact(20)

  
```{r child = "chapter4.Rmd"}
```

***

CHAPTER 4

## CHAPTER 4

I followed all the steps of DataCamp excercise, trying to repeat the same procedures in RStudio. Some of them worked well, but, as you can see, some of them didn't. For example: I couldn't get any graphics visible in GitHub. Instead I kept on receiving following emails:

"The page build failed for the `master` branch with the following error: The file `chapter4.Rmd` is not properly UTF-8 encoded."

Anyway, I listed some of my practises even though they weren't always very succesful. Keep on working..

Task 2:

Boston data has 14 columns (variables) and 506 rows (cases)


Task 3:

Visualizations don't show up in my GitHub. (What do I do wrong?)



Task 4:

Standardization changes variables so that mean = 0 and sd is constant, so variables are easy to use in many statistical analyzis. 


      crim                 zn               indus        
 Min.   :-0.419367   Min.   :-0.48724   Min.   :-1.5563  
 1st Qu.:-0.410563   1st Qu.:-0.48724   1st Qu.:-0.8668  
 Median :-0.390280   Median :-0.48724   Median :-0.2109  
 Mean   : 0.000000   Mean   : 0.00000   Mean   : 0.0000  
 3rd Qu.: 0.007389   3rd Qu.: 0.04872   3rd Qu.: 1.0150  
 Max.   : 9.924110   Max.   : 3.80047   Max.   : 2.4202  
      chas              nox                rm         
 Min.   :-0.2723   Min.   :-1.4644   Min.   :-3.8764  
 1st Qu.:-0.2723   1st Qu.:-0.9121   1st Qu.:-0.5681  
 Median :-0.2723   Median :-0.1441   Median :-0.1084  
 Mean   : 0.0000   Mean   : 0.0000   Mean   : 0.0000  
 3rd Qu.:-0.2723   3rd Qu.: 0.5981   3rd Qu.: 0.4823  
 Max.   : 3.6648   Max.   : 2.7296   Max.   : 3.5515  
      age               dis               rad         
 Min.   :-2.3331   Min.   :-1.2658   Min.   :-0.9819  
 1st Qu.:-0.8366   1st Qu.:-0.8049   1st Qu.:-0.6373  
 Median : 0.3171   Median :-0.2790   Median :-0.5225  
 Mean   : 0.0000   Mean   : 0.0000   Mean   : 0.0000  
 3rd Qu.: 0.9059   3rd Qu.: 0.6617   3rd Qu.: 1.6596  
 Max.   : 1.1164   Max.   : 3.9566   Max.   : 1.6596  
      tax             ptratio            black        
 Min.   :-1.3127   Min.   :-2.7047   Min.   :-3.9033  
 1st Qu.:-0.7668   1st Qu.:-0.4876   1st Qu.: 0.2049  
 Median :-0.4642   Median : 0.2746   Median : 0.3808  
 Mean   : 0.0000   Mean   : 0.0000   Mean   : 0.0000  
 3rd Qu.: 1.5294   3rd Qu.: 0.8058   3rd Qu.: 0.4332  
 Max.   : 1.7964   Max.   : 1.6372   Max.   : 0.4406  
     lstat              medv        
 Min.   :-1.5296   Min.   :-1.9063  
 1st Qu.:-0.7986   1st Qu.:-0.5989  
 Median :-0.1811   Median :-0.1449  
 Mean   : 0.0000   Mean   : 0.0000  
 3rd Qu.: 0.6024   3rd Qu.: 0.2683  
 Max.   : 3.5453   Max.   : 2.9865  




Print of the quantile -function:

          0%          25%          50% 
-0.419366929 -0.410563278 -0.390280295 
         75%         100% 
 0.007389247  9.924109610 
 
 Table of the new factor crime:
 
 crime
     low  med_low med_high     high 
     127      126      126      127 

Number of rows in train set: 404


Task 5:

n <- nrow(boston_scaled)
n
ind <-sample(n, size = n * 0.8)
train <- boston_scaled[ind,]
test <- boston_scaled[-ind,]
nrow(test)
nrow(train)
lda.fit <- lda(crim ~ ., data = train)
lda.fit
plot(lda.fit, dim = 2) 

I can see graphics in R, but not in GitHub, where's the problem?

Task 6:

I didn't figure out how to: "Save the crime categories from the test set and then remove the categorical crime variable from the test dataset." Without that the cross tabulation didn't work.

lda.pred <- predict(lda.fit, newdata = test)
table(correct = correct_classes, predicted = lda.pred$class)

DataCamp cross tabulation has 73 correct prediction out of 94, which means about 78 percent.

Task 7:

The first step would have been "Reload the Boston dataset", but I couldn't do it.

Error in summary(Boston) : object 'Boston' not found


